Network based multifactorial modelling microRNA-target interaction.

### 2019-12-09 NAR_form_article.Rmd
revise last paragraph

## Simulation of large and realistic network

@@

# Additions to be fixed

Additionally, miRNA:gene expression dataset which was integrated via miRTarBase [@chou2017mirtarbase] was analysed in mean of perturbation efficiency to determine crucial genes on the network. We have observed that two miRNAs and 488 genes are effective in terms of perturbation efficiency, when we ran our model with more than 15% efficiency on target expression. miR-10b was investigated via HMDD database [@huang2018hmdd] and mostly found as metastatic biomarker. On the other hand, it was observed that miR-148a is critical for promotion of apoptosis and supression of breast cancer cell growth. Additionaly, to obtain the number of genes in a narrow range, the model was ran with 17% efficency on target expression and 297 genes and one miRNA were observed as highly perturbation-effective. We analysed these genes via eDGAR, a database of Disease-Gene Associations with annotated Relationships among genes [@babbi2017edgar] that supplies different observations about crucial genes such as direct physical interactions, other shared genes with these interactions, protein-protein interactions, GO terms etc.  With our model, we obtained 3 (TP53, BRCA1, AKT1) of 27 critical breast cancer genes and these genes show direct physical interaction with 21 genes. 33 shared genes which are observed on these direct interactions were also found in our effective perturbation elements.We have obtained 7 (KLF4, TP53, BRCA1, CREB, ID4, GATA3, CTBP1) transcription factors (TFs) that are common in 44 critical TFs which are provided by eDGAR dataset. 44 of regulated genes via these TFs were found in our highly effective genes. it has been observed that these genes cover 22.5% of 297 perturbation-effective genes.

>>>>

## Simulation of a large and realistic network

@@

# Genes causing widespread perturbation

Additionally, miRNA:gene expression dataset which was integrated via miRTarBase [@chou2017mirtarbase] was analysed in mean of perturbation efficiency to determine crucial genes on the network. We have observed that one miRNA and 297 genes have high perturbation efficiency, when we ran our model with more than 17% efficiency on target expression. The miRNA, miR-10b was investigated via HMDD database [@huang2018hmdd] and was found as metastatic biomarker. The genes with high perturbation efficiency were analysed via eDGAR, a database of Disease-Gene Associations with annotated relationships among genes [@babbi2017edgar] that supplies different observations about crucial genes such as direct physical interactions, other shared genes with these interactions, protein-protein interactions, GO terms etc.  With our model, we obtained 3 (TP53, BRCA1, AKT1) of 27 critical breast cancer genes and these genes show direct physical interaction with 21 genes. 33 shared genes which are observed on these direct interactions were also found in our effective perturbation elements. We have obtained 7 (KLF4, TP53, BRCA1, CREB, ID4, GATA3, CTBP1) transcription factors (TFs) that are common in 44 critical TFs which are provided by eDGAR dataset. 44 of regulated genes via these TFs were found in our highly effective genes. it has been observed that these genes cover 22.5% of 297 perturbation-effective genes.
